Generation of Variation and Mean Fitness Increase: \\ Necessity is the Mother of Genetic Invention

### 2017-11-29 ms.tex
small change by MWF

Now, applying Result~\ref{result:mfp} (eq.~\ref{eq:mfp_sign}) to Eq.~\ref{eq:Lex}, the sign of the derivative of $\lambda_1$ with respect to $\tilde{C_k}$ is
\begin{equation}
sign \frac{\partial \lambda_1}{\partial \tilde{C}_k} =
sign\Big(\lambda_1 - \frac{w_k}{\hat{\bar w}}\Big).
\end{equation}
Thus
\begin{multline}
sign \frac{\partial \lambda_1}{\partial \tilde{C}_k}\bigg\rvert_{\tilde{C}_k = C_k} = 
sign\Big(1 - \frac{w_k}{\hat{\bar w}}\Big) =  
sign(\hat{\bar w} - w_k),
\end{multline}
since $\hat{\bar w}>0$.
This completes the proof.
\end{proof}

@@

Note that if the modifier has the same effect on all types,
then we can substitute $C = \mu I$ (with $\mu > 0$) in Eq.~\ref{eq:model_equilibrium}, and proceeding as in Eq.~\ref{eq:mfp_K}, we find a relationship previously described by~\citet[eq.~24]{Hermisson2002},
\begin{equation}\label{eq:mutational_loss}
\frac{\partial \hat{\bar{w}}}{\partial \mu} = 
-\frac{1}{\mu}\Big(\sum_{k=1}^{n} \hat u_k \hat v_k w_k - \hat{\bar{w}} \Big) = -\frac{1}{\mu} G,
\end{equation}
where $G$, equal to the difference between the \emph{ancestral mean fitness} $(\sum_{k=1}^{n} \hat u_k \hat v_k w_k)$ and the \emph{stable population mean fitness} $(\hat{\bar{w}})$ when $C_k=\mu$, is  called the \emph{mutational loss}~\citep{Hermisson2002}.

>>>>

Now, applying Result~\ref{result:mfp} (eq.~\ref{eq:mfp_sign}) to Eq.~\ref{eq:Lex}, the sign of the derivative of $\lambda_1$ with respect to $\tilde{C_k}$ is
\begin{equation}
sign \frac{\partial \lambda_1}{\partial \tilde{C}_k} =
sign\left(\lambda_1 - \frac{w_k}{\hat{\bar w}}\right).
\end{equation}
Thus
\begin{multline}
sign \left.\frac{\partial \lambda_1}{\partial \tilde{C}_k}\right\rvert_{\tilde{C}_k = C_k} = 
sign\left(1 - \frac{w_k}{\hat{\bar w}}\right) =  
sign(\hat{\bar w} - w_k),
\end{multline}
since $\hat{\bar w}>0$.
This completes the proof.
\end{proof}

@@

Note that if the modifier has the same effect on all types,
then we can substitute $C = \mu I$ (with $\mu > 0$) in Eq.~\ref{eq:model_equilibrium}, and proceeding as in Eq.~\ref{eq:mfp_K}, we find a relationship previously described by~\citet[eq.~24]{Hermisson2002},
\begin{equation}\label{eq:mutational_loss}
\frac{\partial \hat{\bar{w}}}{\partial \mu} = 
-\frac{1}{\mu}\left(\sum_{k=1}^{n} \hat u_k \hat v_k w_k - \hat{\bar{w}} \right) = -\frac{1}{\mu} G,
\end{equation}
where $\hat u_k$ and $\hat v_k$ are computed at the equilibrium associated with $\mu$ and $\hat{\bar{w}}$ is the mean fitness at that equilibrium.
$G$, the difference between the \emph{ancestral mean fitness} $(\sum_{k=1}^{n} \hat u_k \hat v_k w_k)$ and the \emph{stable population mean fitness} $(\hat{\bar{w}})$ when $C_k=\mu$, is  called the \emph{mutational loss}~\citep{Hermisson2002}.
